### 2018-06-14 express2018/related.tex
Make some more spaces

Beside Nesi, there're three other CCS formalisations. One
is done in Isabelle/HOL (based on Nominal datatypes) in 2010, by Jesper Bengtson as part of his PhD
thesis project \cite{bengtson2010formalising}, available in Isabelle's Archive of Formal
Proofs (AFP) \footnote{\url{https://www.isa-afp.org/entries/CCS.html}}. He has formalized
classic properties for strong/weak equivalence and observational
congruence, however the CCS grammar doesn't include process constants
(or recursion operators), and the proved theorems also look quite
different with their forms in textbooks. On the other side, Jesper
Bengtson and Joachim Parrow made great progress on pi-calculus formalization and
proved that the algebraic axiomatization of bisimulation
equivalence in the pi-calculus is sound and complete. \cite{bengtson2007completeness}
The other formalisation is based on Coq, done by Solange
Coupet-Grimal in 1995, which is part of the
``coq-contribs'' archive (Coq's official user contributed code)
\footnote{\url{https://github.com/coq-contribs/ccs}}. This is actually
a formalisation of transition systems without any algebraic operator,
and covers the very basic properties of strong/weak equivalence and observational
congruence. The last one was done by Chaudhuri et
al. \cite{chaudhuri2014formalization} using Abella, this work
particularily focus on bisimulation up to techniques while the CCS
type doesn't have restriction, recursion and relabelling operators.

>>>>

Beside Nesi, there exist other CCS formalisations. One
is done in Isabelle/HOL (based on Nominal datatypes) in 2010, by Jesper Bengtson as part of his PhD
thesis project \cite{bengtson2010formalising}, available in Isabelle's Archive of Formal
Proofs (AFP) \footnote{\url{https://www.isa-afp.org/entries/CCS.html}}. He has formalized
classic properties for strong/weak equivalence and observational
congruence, however the CCS grammar doesn't include process constants
(or recursion operators), and the proved theorems also look quite
different with their forms in textbooks.%
%  On the other side, Jesper
% Bengtson and Joachim Parrow made great progress on pi-calculus formalization and
% proved that the algebraic axiomatization of bisimulation
% equivalence in the pi-calculus is sound and complete. \cite{bengtson2007completeness}
The other formalisation is based on Coq, done by Solange
Coupet-Grimal in 1995, which is part of the
``coq-contribs'' archive (Coq's official user contributed code)
\footnote{\url{https://github.com/coq-contribs/ccs}}. This is actually
a formalisation of transition systems without any algebraic operator,
and covers the very basic properties of strong/weak equivalence and observational
congruence. The last one was done by Chaudhuri et
al. \cite{chaudhuri2014formalization} using Abella, this work
particularily focus on bisimulation up to techniques while the CCS
type doesn't have restriction, recursion and relabelling operators.
